
\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}
\renewcommand\lstlistingname{Algorithm}
\renewcommand\lstlistlistingname{Algorithms}
\def\lstlistingautorefname{Alg.}

\lstdefinestyle{Python}{
    language        = Python,
    frame           = lines, 
    basicstyle      = \footnotesize,
    keywordstyle    = \color{blue},
    stringstyle     = \color{green},
    commentstyle    = \color{red}\ttfamily
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}



\pagestyle{fancyplain}
\headheight 35pt
                 % ENTER REVIEW NUMBER HERE %
\chead{\textbf{\large Review-10}}
           % ################################### %

\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

\begin{document}                 % ENTER PAPER TITLE HERE %
\begin{center}
  \large{Counterfactual Data Augmentation using Locally Factored Dynamics}
\end{center}
           % ################################### %

Various dynamic processes in robot control consist of subprocesses which interact with each other during the execution of the global process. Sparse interactions between subprocesses allows the formulation of locally independent mechanisms for globally optimal behavior. The work proposes a novel model-free data augmentation framework by conditioning on locally factored dynamics which aid in the generation of causally valid counterfactual experiences. Counterfactual Data Augmentation (CoDA) leverages causal independence in interactions to factor local dynamics in an object-oriented manner. Improved performance of model-free agents trained on counterfactual experiences validates the suitability of CoDA in batch-constrained and goal-conditioned settings. 

CoDA makes use of sparse interactions between objects in the environment to locally factor the dyanmics. Given a graphical structure of environment interactions, object entities maybe considered locally independent if the interactions between them are limited over successive timesteps. This leads to a decomposition of state and action spaces which is based on the minimality assumption of the environment as a factored MDP. Connected edges in the factored MDP depict local interactions which can causally model new transitions in independent subspaces. CoDA is implemented as a function of two factual transitions and mask function which yield a causal transition in the same local subspace as the original transitions. This bound is validated by making use of structured equations in local neighborhood. Practical implementation of CoDA makes use of attention masks in a tranformer setting. The framework is trained to infer local factorization instead of sampling future states as in model-based RL. 

Contrary to typical model-free frameworks, CoDA aims to improve data-efficiency in RL by leveraging aspects of the environment dynamics. The problem of modelling local independence in cuasal structures is an interesting and novel direction which depicts improvement in comparison to learned models of the environment. However, the method presents two aspects with room for improvement. Firstly, the learned variant of CoDA lags behind the variant with access to ground truth. This indicates that the model formed by counterfactual experiences may not be a complete and accurate representation of practical scenarios. A more rigorous validation on real-world robot tasks would aid in better evaluation of the proposed scheme. Secondly, increasing the amount of state factors in batch RL only leads to little increment in success rates when compared to the extensive addition of data and model scale. This depicts a lack of local dynamic information contained in the factorization scheme. A potential improvement could consist of learning factorizations based on information theoretic measures such as maximization of mutual information between counterfactual and local dynamics. 



\end{document}
